R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-08 manuscript.Rmd
update manuscript.pdf, remove queue download section not going to discuss since not done

      Background. The number of individuals of each species in
        a given location forms the basis for many sub-fields of ecology and
        evolution. Data on individuals, including which species, and
        where they're found, can be used for a large number of research
        questions. Global Biodiversity Information Facility (hereafter, GBIF)
        is the largest of these. Programmatic clients for GBIF would
        make research dealing with GBIF data much easier.

@@

      Results. For all clients we describe their design and utility,
        and demonstrate many use cases.

      Discussion. Programmatic acccess to GBIF will facilitate more open
        and reproducible science. We hope that all scientists using GBIF
        data will do so with one of these two clients.

@@

#### Queueing Download Requests

FILL IN TEXT HERE ...

>>>>

      Background. The number of individuals of each species in
        a given location forms the basis for many sub-fields of ecology and
        evolution. Data on individuals, including which species, and
        where they're found can be used for a large number of research
        questions. Global Biodiversity Information Facility (hereafter, GBIF)
        is the largest of these. Programmatic clients for GBIF would
        make research dealing with GBIF data much easier and more reproducible.

@@

      Results. For all clients we describe their design and utility,
        and demonstrate some use cases.

      Discussion. Programmatic acccess to GBIF will facilitate more open
        and reproducible science - the three GBIF clients described herein
        are a significant contribution towards this goal.

@@

### 2017-09-08 manuscript.tex
update manuscript.pdf, remove queue download section not going to discuss since not done

  Results. For all clients we describe their design and utility, and
  demonstrate many use cases.

  Discussion. Programmatic acccess to GBIF will facilitate more open and
  reproducible science. We hope that all scientists using GBIF data will
  do so with one of these two clients.
  \end{abstract}

@@

Dataset metrics are another useful way of figuring out what datasets you
may want to use. One drawback is that these metrics data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (21522).

@@

\paragraph{Queueing Download Requests}\label{queueing-download-requests}

FILL IN TEXT HERE \ldots{}

>>>>

  Results. For all clients we describe their design and utility, and
  demonstrate some use cases.

  Discussion. Programmatic acccess to GBIF will facilitate more open and
  reproducible science - the three GBIF clients described herein are a
  significant contribution towards this goal.
  \end{abstract}

@@

Dataset metrics are another useful way of figuring out what datasets you
may want to use. One drawback is that these metrics data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (21534).

@@
